Jaigo Technical Report

### 2007-12-19 trunk/paper/paper.tex
refactor column alignment spec, and apply it to both tables

\tref{table:first50} shows the first 50 moves on a 19x19 board with human (black) versus crawler (white).
\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time (ms) & Time (ms) & Avg (ms) & Min (ms) & Max (ms) & File\\ \midrule
      (no name) & 109675 & 25.68 & 14310.594 &	36908.812 &	0.337 &	0.059	& 1593.542	& simple\_go.js (line 407)\\
      flood\_mark & 1618 & 14.17 & 7897.73 & 25481.245 & 15.749 & 0.162 & 1635.18 & simple\_go.js (line 807)\\
      (no name) &	194678 &	11.75	& 6551.626 &	6554.733 &	0.034 &	0.008 &	1555.243 &	simple\_go.js (line 819)\\
      string\_as\_move &	56065 &	7.48 &	4168.485 &	4169.549 &	0.074 &	0.011 &	1591.844 &	simple\_go.js (line 192)\\
      iterate	& 109676 &	7.19 &	4005.749 &	22595.463 &	0.206 &	0.011 &	1593.499 &	simple\_go.js (line 391)\\
      (no name) &	283642 &	4.9 &	2732.499 &	18589.343 &	0.066 &	0.015 &	1593.144 &	simple\_go.js (line 416)\\
      iterateOwnProperties &	5811	& 4.38	& 2440.378 &	2847.852 &	0.49 &	0.004 &	2.917 &	simple\_go.js (line 132)\\
      Set\_Goban &	2150 &	3.53 &	1968.651 &	1969.095 &	0.916 &	0.004 &	942.058 &	simple\_go.js (line 528)\\
      (no name) &	42734 &	2.99 &	1666.478 &	1666.716 &	0.039 &	0.008 &	935.83 &	simple\_go.js (line 835)\\
      update &	3662 &	2.9 &	1613.61 &	1614.099 &	0.441 &	0.004 &	1560.416 &	simple\_go.js (line 117)\\
      Add\_Block &	2340 &	2.8 &	1559.92 &	1560.774 &	0.667 &	0.007 &	1529.63 &	simple\_go.js (line 757)\\
      Calculate\_Neighbour &	448 &	2.67 &	1487.337 &	12205.939 &	27.245 &	0.019 &	1579.849 &	simple\_go.js (line 829)\\
      Simple\_Same\_Block &	2149 &	1.93 &	1073.573 &	8185.472 &	3.809 &	0.002 &	1556.376 &	simple\_go.js (line 606)\\
      List\_Block\_Liberties &	3210 &	1.56 &	871.609 &	5057.619 &	1.576 &	0.012 &	1593.058 &	simple\_go.js (line 863)\\ \bottomrule
  \end{tabular}}
  \caption{First 50 moves on a 19x19 board}
  \label{table:first50}
\end{table}

@@

\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\	\midrule
      (no name) &	404494 &	32.8 &	71255.203 &	147518.241 &	0.365 &	0.059 &	1650.149 &	simple\_go.js (line 407)\\
      flood\_mark &	3838 &	15.94 &	34634.022 &	96713.52 &	25.199 &	0.206 &	1736.537 &	simple\_go.js (line 807)\\
      iterate &	404495 &	8.75 &	19004.696 &	76254.33 &	0.189 &	0.011 &	1650.101 &	simple\_go.js (line 391)\\
      (no name) &	735190 &	8.72 &	18941.197 &	18941.987 &	0.026 &	0.008 &	1572.648 &	simple\_go.js (line 819)\\
      string\_as\_move &	242765 &	5.86 &	12724.373	& 12725.279 &	0.052 &	0.011 &	1629.186 &	simple\_go.js (line 192)\\
      (no name) &	1041519 &	4.7 &	10209.513 &	57248.372 &	0.055 &	0.015 &	1649.869 &	simple\_go.js (line 416)\\
      List\_Block\_Liberties &	7706 &	4.02 &	8727.331 &	21457.809 &	2.785 &	0.013 &	1630.607 &	simple\_go.js (line 863)\\
      iterateOwnProperties &	14752 &	3.68 &	7985.019 &	9340.503 &	0.633 &	0.004 &	2.419 &	simple\_go.js (line 132)\\
      update &	8742 &	3.18 &	6911.102 &	6911.93 &	0.791 &	0.004 &	1648.007 &	simple\_go.js (line 117)\\
      Calculate\_Neighbour &	661 &	3.03 &	6593.032 &	60385.478 &	91.355 &	0.115 &	1679.244 &	simple\_go.js (line 829)\\
      (no name) &	160414 &	2.51 &	5444.827 &	5445.809 &	0.034	& 0.008 &	944.464 &	simple\_go.js (line 835)\\
      Add\_Stone &	6010 &	1.1 &	2392.214	& 191461.602	& 31.857 &	1.524 &	1785.447 &	simple\_go.js (line 641)\\ \bottomrule
    \end{tabular}}
  \caption{First 100 moves on a 19x19 board}
  \label{table:first100}
\end{table}

@@

On an iPhone over 54mbps 802.11g wifi with a full signal connected to a 3mbps cable modem, the median jaigo load time was 5 seconds, with the initial load time being the longest measurement at 15 seconds. On an iPhone over AT\&T 2.5G EDGE with a full signal, the median jaigo load time was 21 seconds, with a low of 17 seconds and a high of 30 seconds.

Median move times in other go engines (gnugo especially)?

\chapter{Recommendations, especially for future work and unsolved issues}
We feel that the choice of browser is more important than the choice of computing platform for the performance of jaigo. Our anecdotal experience and those of others on the Web show that there is an order of magnitude difference between popular browsers for some JavaScript operations. However, we have not carefully studied this issue.%http://therealcrisp.xs4all.nl/blog/2006/12/09/string-performance-in-internet-explorer/

>>>>

\tref{table:first50} shows the first 50 moves on a 19x19 board with human (black) versus crawler (white).
\newcolumntype{M}{D{.}{.}{3}}
\begin{table}
  \rotatebox{90}{%  fc%         own       time      avg       min       max file
    \begin{tabular}{lrD{.}{.}{2}MMMMMl} \toprule
      Function & Calls & \multicolumn{1}{c}{Percent} & \multicolumn{1}{c}{Own Time (ms)} & \multicolumn{1}{c}{Time (ms)} & \multicolumn{1}{c}{Avg (ms)} & \multicolumn{1}{c}{Min (ms)} & \multicolumn{1}{c}{Max (ms)} & File\\ \midrule
      (no name) & 109675 & 25.68 & 14310.594 &	36908.812 &	0.337 &	0.059	& 1593.542	& simple\_go.js (line 407)\\
      flood\_mark & 1618 & 14.17 & 7897.73 & 25481.245 & 15.749 & 0.162 & 1635.18 & simple\_go.js (line 807)\\
      (no name) &	194678 &	11.75	& 6551.626 &	6554.733 &	0.034 &	0.008 &	1555.243 &	simple\_go.js (line 819)\\
      string\_as\_move &	56065 &	7.48 &	4168.485 &	4169.549 &	0.074 &	0.011 &	1591.844 &	simple\_go.js (line 192)\\
      iterate	& 109676 &	7.19 &	4005.749 &	22595.463 &	0.206 &	0.011 &	1593.499 &	simple\_go.js (line 391)\\
      (no name) &	283642 &	4.9 &	2732.499 &	18589.343 &	0.066 &	0.015 &	1593.144 &	simple\_go.js (line 416)\\
      iterateOwnProperties &	5811	& 4.38	& 2440.378 &	2847.852 &	0.49 &	0.004 &	2.917 &	simple\_go.js (line 132)\\
      Set\_Goban &	2150 &	3.53 &	1968.651 &	1969.095 &	0.916 &	0.004 &	942.058 &	simple\_go.js (line 528)\\
      (no name) &	42734 &	2.99 &	1666.478 &	1666.716 &	0.039 &	0.008 &	935.83 &	simple\_go.js (line 835)\\
      update &	3662 &	2.9 &	1613.61 &	1614.099 &	0.441 &	0.004 &	1560.416 &	simple\_go.js (line 117)\\
      Add\_Block &	2340 &	2.8 &	1559.92 &	1560.774 &	0.667 &	0.007 &	1529.63 &	simple\_go.js (line 757)\\
      Calculate\_Neighbour &	448 &	2.67 &	1487.337 &	12205.939 &	27.245 &	0.019 &	1579.849 &	simple\_go.js (line 829)\\
      Simple\_Same\_Block &	2149 &	1.93 &	1073.573 &	8185.472 &	3.809 &	0.002 &	1556.376 &	simple\_go.js (line 606)\\
      List\_Block\_Liberties &	3210 &	1.56 &	871.609 &	5057.619 &	1.576 &	0.012 &	1593.058 &	simple\_go.js (line 863)\\ \bottomrule
  \end{tabular}}
  \caption{First 50 moves on a 19x19 board}
  \label{table:first50}
\end{table}

@@

\begin{table}
  \rotatebox{90}{
    \begin{tabular}{lrD{.}{.}{2}MMMMMl} \toprule
      Function & Calls & \multicolumn{1}{c}{Percent} & \multicolumn{1}{c}{Own Time (ms)} & \multicolumn{1}{c}{Time (ms)} & \multicolumn{1}{c}{Avg (ms)} & \multicolumn{1}{c}{Min (ms)} & \multicolumn{1}{c}{Max (ms)} & File\\ \midrule
      (no name) &	404494 &	32.8 &	71255.203 &	147518.241 &	0.365 &	0.059 &	1650.149 &	simple\_go.js (line 407)\\
      flood\_mark &	3838 &	15.94 &	34634.022 &	96713.52 &	25.199 &	0.206 &	1736.537 &	simple\_go.js (line 807)\\
      iterate &	404495 &	8.75 &	19004.696 &	76254.33 &	0.189 &	0.011 &	1650.101 &	simple\_go.js (line 391)\\
      (no name) &	735190 &	8.72 &	18941.197 &	18941.987 &	0.026 &	0.008 &	1572.648 &	simple\_go.js (line 819)\\
      string\_as\_move &	242765 &	5.86 &	12724.373	& 12725.279 &	0.052 &	0.011 &	1629.186 &	simple\_go.js (line 192)\\
      (no name) &	1041519 &	4.7 &	10209.513 &	57248.372 &	0.055 &	0.015 &	1649.869 &	simple\_go.js (line 416)\\
      List\_Block\_Liberties &	7706 &	4.02 &	8727.331 &	21457.809 &	2.785 &	0.013 &	1630.607 &	simple\_go.js (line 863)\\
      iterateOwnProperties &	14752 &	3.68 &	7985.019 &	9340.503 &	0.633 &	0.004 &	2.419 &	simple\_go.js (line 132)\\
      update &	8742 &	3.18 &	6911.102 &	6911.93 &	0.791 &	0.004 &	1648.007 &	simple\_go.js (line 117)\\
      Calculate\_Neighbour &	661 &	3.03 &	6593.032 &	60385.478 &	91.355 &	0.115 &	1679.244 &	simple\_go.js (line 829)\\
      (no name) &	160414 &	2.51 &	5444.827 &	5445.809 &	0.034	& 0.008 &	944.464 &	simple\_go.js (line 835)\\
      Add\_Stone &	6010 &	1.1 &	2392.214	& 191461.602	& 31.857 &	1.524 &	1785.447 &	simple\_go.js (line 641)\\ \bottomrule
    \end{tabular}}
  \caption{First 100 moves on a 19x19 board}
  \label{table:first100}
\end{table}

@@

On an iPhone over 54mbps 802.11g wifi with a full signal connected to a 3mbps cable modem, the median jaigo load time was 5 seconds, with the initial load time being the longest measurement at 15 seconds. On an iPhone over AT\&T 2.5G EDGE with a full signal, the median jaigo load time was 21 seconds, with a low of 17 seconds and a high of 30 seconds.
%TODO: Median move times in other go engines (gnugo especially)?

\chapter{Recommendations, future work, and unsolved issues}
We feel that the choice of browser is more important than the choice of computing platform for the performance of jaigo. Our anecdotal experience and those of others on the Web show that there is an order of magnitude difference between popular browsers for some JavaScript operations. However, we have not carefully studied this issue.%http://therealcrisp.xs4all.nl/blog/2006/12/09/string-performance-in-internet-explorer/
